---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
candy_clean <- read_csv(here::here("clean_data/clean_data.csv"))
```

Q1:

What is the total number of candy ratings given across the three years.
(Number of candy ratings, not the number of raters. Don’t count missing values)

```{r}
candy_clean %>% 
  summarise(total_ratings = sum(!is.na(feeling)))
  
```

Q2: What was the average age of people who are going out trick or treating?

```{r}
candy_clean %>% 
  filter(trick_or_treating == "Yes") %>% 
  summarise(mean_age = mean(age))
```

Q3: What was the average age of people who are not going trick or treating?

```{r}
candy_clean %>% 
  filter(trick_or_treating == "No") %>% 
  summarise(mean_age = mean(age))
```

Q4: For each of joy, despair and meh, which candy bar received the most of these ratings?

```{r}
candy_clean %>% 
  filter(feeling == "JOY") %>% 
  group_by(candy) %>% 
  summarise(total = n()) %>% 
  slice_max(total, n = 1)

candy_clean %>% 
  filter(feeling == "MEH") %>% 
  group_by(candy) %>% 
  summarise(total = n()) %>% 
  slice_max(total, n = 1)
  
candy_clean %>% 
  filter(feeling == "DESPAIR") %>% 
  group_by(candy) %>% 
  summarise(total = n()) %>% 
  slice_max(total, n = 1) %>% 
  pull()

```


Q5:
How many people rated Starburst as despair?

```{r}
candy_clean %>% 
  filter(candy == "starburst") %>% 
  filter(feeling == "DESPAIR") %>% 
  summarise(n())
```
For the next three questions, count despair as -1, joy as +1, and meh as 0

```{r}
net_feelies <- candy_clean %>% 
  mutate(feeling = as.numeric(case_when(feeling == "JOY" ~ 1,
                             feeling == "DESPAIR" ~ -1,
                             feeling == "MEH" ~ 0)))
```


Q6:
What was the most popular candy bar by this rating system for each gender in the dataset ?

```{r}
net_feelies %>% 
  filter(gender == "Male") %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```
```{r}
net_feelies %>% 
  filter(gender == "Female") %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```

```{r}
net_feelies %>% 
  filter(gender == "Other") %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```

Q7:
What was the most popular candy bar in each year?

```{r}
net_feelies %>% 
  filter(year == 2015) %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```
```{r}
net_feelies %>% 
  filter(year == 2016) %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```

```{r}
net_feelies %>% 
  filter(year == 2017) %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```



Q8:
What was the most popular candy bar by this rating for people in US, Canada, UK, and all other countries?

```{r}
net_feelies %>% 
  filter(country == "us") %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```
```{r}
net_feelies %>% 
  filter(country == "canada") %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```
```{r}
net_feelies %>% 
  filter(country == "uk") %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```

```{r}
net_feelies %>% 
  filter(!country %in% c("canada", "us", "uk")) %>% 
  group_by(candy) %>% 
  summarise(net_feel = sum(feeling, na.rm = TRUE)) %>% 
  slice_max(net_feel, n = 1)
```

